Radiance - A Web Application Environment

### 2016-12-16 els2017-radiance/paper.tex
Renamed files.
Don't overflow

\documentclass{sig-alternate-05-2015}
\usepackage[english]{babel}
\usepackage{float}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{minted}
\usemintedstyle{autumn}
\bibliographystyle{abbrv}

@@

With these routes in place, our previous example URL will be translated into \texttt{hello/index} as required. Furthermore, the requested reversal translation of the URI \\\texttt{/static/hello/index.css} will be turned into the URL \\\texttt{http://radiance.example.com/test/static/hello/index.css}, completing the cycle properly. \\

>>>>

\documentclass{sig-alternate}
\usepackage[english]{babel}
\usepackage{float}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{minted}
\usemintedstyle{autumn}
\bibliographystyle{abbrv}

@@

With these routes in place, our previous example URL will be translated into \texttt{hello/index} as required. Furthermore, the requested reversal translation of the URI \\\texttt{/static/hello/index.css} will be turned into the URL \\\texttt{\small http://radiance.example.com/test/static/hello/index.css},\\ completing the cycle properly. \\
